#Predict prices of a product using regression and model

The following example shows that we can build the slope using the statstics on the prices 
and get the coefficients of the price change. After finding the coefficients we can predict 
the inputed items(with weight) prices using the model.   

---
## Example
### `diamond` data set from `UsingR` 
Data is diamond prices (Singapore dollars) and diamond weight
in carats (standard measure of diamond mass, 0.2 $g$). To get the data use `library(UsingR); data(diamond)`


---
## Plot of the data
```{r, echo = FALSE, fig.height=5,fig.width=5}
library(UsingR)
data(diamond)
library(ggplot2)
g = ggplot(diamond, aes(x = carat, y = price))
g = g + xlab("Mass (carats)")
g = g + ylab("Price (SIN $)")
g = g + geom_point(size = 7, colour = "black", alpha=0.5)
g = g + geom_point(size = 5, colour = "blue", alpha=0.2)
g = g + geom_smooth(method = "lm", colour = "black")
g
```

---
## Fitting the linear regression model
```{r}
fit <- lm(price ~ carat, data = diamond)
coef(fit)
```

* We estimate an expected `r round(coef(fit)[2], 2)` (SIN) dollar increase in price for every carat increase in mass of diamond.
* The intercept `r round(coef(fit)[1], 2)` is the expected price
  of a 0 carat diamond.

---
## Getting a more interpretable intercept
```{r, echo = TRUE}
fit2 <- lm(price ~ I(carat - mean(carat)), data = diamond)
coef(fit2)
```

Thus $`r round(coef(fit2)[1], 1)` is the expected price for 
the average sized diamond of the data (`r mean(diamond$carat)` carats).

---
## Changing scale
* A one carat increase in a diamond is pretty big, what about
  changing units to 1/10th of a carat? 
* We can just do this by just dividing the coeficient by 10.
  * We expect  a `r round(coef(fit)[2], 2) / 10` (SIN) dollar   change in price for every 1/10th of a carat increase in mass of diamond.
* Showing that it's the same if we rescale the Xs and refit
```{r, echo = TRUE}
fit3 <- lm(price ~ I(carat * 10), data = diamond)
coef(fit3)
```

---
# Predicting the price of a diamond
```{r, echo = TRUE}
newx <- c(0.16, 0.27, 0.34)
coef(fit)[1] + coef(fit)[2] * newx                  #using the coeff
predict(fit, newdata = data.frame(carat = newx))    #same but using the internal predict fun
```

---
Predicted values at the observed Xs (red)
and at the new Xs (lines)
```{r, echo = FALSE, fig.height=5,fig.width=5}
data(diamond)
plot(diamond$carat, diamond$price,  
     xlab = "Mass (carats)", 
     ylab = "Price (SIN $)", 
     bg = "lightblue", 
     col = "black", cex = 1.1, pch = 21,frame = FALSE)
abline(fit, lwd = 2)
points(diamond$carat, predict(fit), pch = 19, col = "red")
lines(c(0.16, 0.16, 0.12), 
      c(200, coef(fit)[1] + coef(fit)[2] * 0.16,
      coef(fit)[1] + coef(fit)[2] * 0.16))
lines(c(0.27, 0.27, 0.12), 
      c(200, coef(fit)[1] + coef(fit)[2] * 0.27,
        coef(fit)[1] + coef(fit)[2] * 0.27))
lines(c(0.34, 0.34, 0.12), 
      c(200, coef(fit)[1] + coef(fit)[2] * 0.34,
        coef(fit)[1] + coef(fit)[2] * 0.34))
text(newx, rep(250, 3), labels = newx, pos = 2)
```
